Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-10-12 pres/conclusion.tex
Final version

\begin{frame}
	\frametitle{Conclusion}
		The neutron group fluxes and reactivity coefficients from Moltres
		(without \gls{DNP} drift) are in
		good agreement with Serpent results, in the context of the \gls{MSFR}.

@@

		\vspace{.3cm}
		Discrepancies in peak neutron
		flux and temperature distributions to other work are primarily due to
		the minor differences in core geometry and using uniform flow instead of
		appling a turbulence model.

		\vspace{.3cm}
		Higher core temperatures observed for start-up fuel composition than
		early-life and equilibrium compositions.

		\vspace{.3cm}
		Discrepancy in average core temperatures during \gls{ULOHS} is mainly due
		to the lack of a decay heat model in Moltres.
\end{frame}

>>>>

\begin{frame}
	\frametitle{Conclusion}
		The neutron group fluxes and reactivity coefficients from Moltres
		(without \gls{DNP} drift) are in
		good agreement with Serpent results.

@@

		\vspace{.3cm}
		Discrepancies present in peak neutron
		flux and temperature distributions relative to other work

		\vspace{.3cm}
		Higher core temperatures observed for start-up fuel composition than
		early-life and equilibrium compositions.
\end{frame}

### 2019-10-12 pres/moltres.tex
Final version

\begin{frame}
	\frametitle{Moltres}
		\textbf{What is Moltres?}
		\begin{itemize}
			\item Moltres is an application code built on the \gls{MOOSE}
			framework, for the simulation of \glspl{MSR}
			\item \gls{MOOSE} is an open source finite element framework written
			in \texttt{C++} that
			relies on Libmesh and PETSc for advanced meshing and PDE solving
			capabilities
			\item Moltres can run transient, implicitly coupled
			neutronics/thermal-hydraulics simulations
			\begin{itemize}
				\item Multi-group neutron diffusion (arbitrary groups)
				\item \gls{DNP} decay (with advection)
				\item Incompressible Navier-Stokes for temperature
				advection-diffusion
				\item 1D, 2D, and 3D modeling are supported
			\end{itemize}
		\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Moltres}
		\textbf{What is Moltres?}
		\begin{itemize}
			\item Moltres \cite{lindsay_introduction_2018} is an application
			built on the \gls{MOOSE} framework, for the simulation of \glspl{MSR}
			\item \gls{MOOSE} \cite{gaston_moose:_2009} is an open source finite
			element framework written in \texttt{C++} that
			relies on Libmesh and PETSc for advanced meshing and PDE solving
			capabilities
			\item Moltres can run transient, implicitly coupled
			neutronics/thermal-hydraulics simulations
			\begin{itemize}
				\item Multi-group neutron diffusion (arbitrary no. of groups)
				\item \gls{DNP} decay (with advection)
				\item Incompressible Navier-Stokes for temperature
				advection-diffusion
				\item 1D, 2D, and 3D modeling are supported
			\end{itemize}
		\end{itemize}
\end{frame}

### 2019-10-12 pres/neutron.tex
Final version

\begin{frame}
	\frametitle{Neutronics Verification}
		\begin{columns}
			\column{5cm}
				\textbf{Serpent Input Parameters}
					\begin{itemize}
						\item 200,000 neutrons per cycle
						\item 50 inactive, 500 active cycles
						\item JEFF-3.1.2 nuclear data library
						\item Six neutron energy groups, eight \gls{DNP} groups
						\item Temperatures defined from 900 K to 1200 K at 50 K
						intervals
					\end{itemize}
			\column{5cm}
				\begin{figure}
					\centering
					\includegraphics[width=\textwidth]
					{../paper/figures/reference}
					\caption{2D axisymmetric model used in Serpent. Derived from
					the \gls{MSFR} reference model
					\cite{fiorina_modelling_2014}.}
					\label{fig:reference}
				\end{figure}
		\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Fuel Composition Data}
			\begin{itemize}
				\item Depletion calculations performed by Rykhlevskii et
				al. \cite{rykhlevskii_fuel_2019}
				\item 60-year depletion calculation on SCALE/TRITON
				using a unit cell representation of the \gls{MSFR} (and
				three other fast-spectrum \glspl{MSR}
				\item U/Th breeder reprocessing scheme
				\item Compositions:
				\begin{itemize}
					\item Start-up: 77.5\% LiF - 19.9\% ThF$_4$
					- 2.6\% UF$_4$
					\item Early-life: 300 days after start-up
					\item Equilibrium: ~43 years after start-up
					($<$3\% change in TRU vector between depletion
					time-steps)
				\end{itemize}
			\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
	\begin{columns}
		\column{5cm}
		\textbf{Moltres Simulation Details}
		\begin{itemize}
			\item Adaptive backward Euler time-stepper
			\item Six neutron groups, eight \gls{DNP} groups
			\item Vacuum neutron boundary condition on outer surfaces
			\item Uniform upward flow of 1.125 m s$^{-1}$
			\item Flow/decay of \glspl{DNP} and heat removal in the outer loop
			is simulated on a simplified 1D geometry separate from active core
			region
			\item Fixed heat removal rate to secondary loop system
		\end{itemize}
		\column{5cm}
		\begin{figure}
			\centering
			\includegraphics[width=.8\textwidth]{../paper/figures/mesh}
			\caption{Mesh of the 2D axisymmetric model used in Moltres. The
			grey and red regions represent the fuel and blanket salt
			respectively.}
			\label{fig:mesh}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Verification}
		\textbf{Results}
			\begin{figure}
				\centering
				\includegraphics[width=.8\textwidth]{../paper/figures/nt-spec}
				\caption{Fine-group and six-group neutron flux distributions
				from Serpent and Moltres (start-up composition without \gls{DNP}
				drift).}
				\label{fig:ntspec}
			\end{figure}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Neutronics Results}
		\begin{columns}
			\column{5cm}
				\textbf{Serpent Input Parameters}
					\begin{itemize}
						\item Neutron population
							\begin{itemize}
								\item 200,000 neutrons per cycle
								\item 50 inactive, 500 active cycles
								\item 5 pcm statistical error in $k_{eff}$
							\end{itemize}
						\item JEFF-3.1.2 nuclear data library
						\item Six neutron energy groups
						\item Eight delayed neutron precursor groups
						\item Temperatures defined from 900 K to 1200 K at 50 K
						intervals
					\end{itemize}
			\column{5.5cm}
				\begin{figure}
					\centering
					\includegraphics[width=\textwidth]
					{./images/reference}
					\caption{2D axisymmetric model used in Serpent. Derived from
					the \gls{MSFR} reference model
					\cite{fiorina_modelling_2014}. (Figure not to scale)}
					\label{fig:reference}
				\end{figure}
		\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Results}
		\textbf{Fuel Composition Data}
			\begin{itemize}
				\item Depletion calculations performed in a previous paper by
				A. Rykhlevskii, B. Betzler, A. Worrall, and K. Huff
				\cite{rykhlevskii_fuel_2019}
				\item 60-year depletion calculation on SCALE/TRITON
				using a unit cell representation of the \gls{MSFR}
				\item U/Th breeder reprocessing scheme
				\begin{itemize}
					\item Th feed, with some $^{233}$U from the blanket rerouted
					to the fuel salt to maintain criticality
				\end{itemize}
				\item Compositions:
				\begin{itemize}
					\item Start-up: LiF - ThF$_4$
					- UF$_4$ (77.5\% - 19.9\% - 2.6\%)
					\item Early-life: 300 days after start-up
					\item Equilibrium: 43 years after start-up
					($<$3\% change in TRU vector between depletion
					time-steps)
				\end{itemize}
			\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Results}
	\begin{columns}
		\column{5.5cm}
		\textbf{Moltres Simulation Details}
		\begin{itemize}
			\small
			\item Adaptive backward Euler time-stepper
			\item Six neutron groups
			\item Eight \gls{DNP} groups
			\item Vacuum neutron boundary condition on outer edges
			\item Uniform upward flow of 1.125 m s$^{-1}$
			\item Flow/decay of \glspl{DNP} and heat removal in the outer loop
			is simulated on a simplified 1D geometry separate from active core
			region
			\item Fixed heat removal rate, $Q_{hx}$, to secondary loop system
		\end{itemize}
		\column{5cm}
		\begin{figure}
			\centering
			\includegraphics[width=\textwidth]{./images/mesh}
			\caption{\footnotesize Mesh of the 2D axisymmetric model used in
			Moltres. The
			grey and red regions represent the fuel and blanket salt
			respectively.}
			\label{fig:mesh}
		\end{figure}
	\end{columns}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Results}
		\textbf{Results}
			\begin{figure}
				\centering
				\includegraphics[width=.8\textwidth]{../paper/figures/nt-spec}
				\caption{Continuous and six energy group neutron flux
				distributions from Serpent and Moltres (start-up composition
				without \gls{DNP} drift at 973 K).}
				\label{fig:ntspec}
			\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Neutronics Results}
		\textbf{Fuel Temperature Reactivity Feedback}
			\begin{table}[t]
				\centering
				\caption{Fuel temperature reactivity feedback coefficients with
				the start-up fuel composition.}
				\begin{tabular}{lccc}
					\hline
					\multirow{2}{*}{Composition} & {$\alpha_T$ [pcm K$^{-1}$]} & {$\alpha_T$ [pcm K$^{-1}$]} & Difference [\%]\\
					& Serpent & Moltres & \\
					\hline
					Start-up & $-7.39 \pm 0.03$ & $-7.46$ & $-0.94$\\
					Early-life & $-7.25 \pm 0.03$ & $-7.33$ & $-1.1$\\
					Equilibrium & $-6.24 \pm 0.03$ & $-6.34$ & $-1.6$\\
					\hline
				\end{tabular}
				\label{table:reactivity}
			\end{table}	
\end{frame}

### 2019-10-12 pres/objectives.tex
presentation mid update
presentation slides first draft
Final version

\begin{frame}
	\frametitle{Objectives}
		\textbf{Objectives}
		\begin{itemize}
			\item Verify the neutronics capabilities in Moltres against Serpent
			\item Demonstrate coupled neutronics/thermal-hydraulics simulations
			of the \gls{MSFR} concept,
			\begin{itemize}
				\item with \gls{BOL}, early-life, and \gls{EOL} fuel compositions
				\item for steady state and transient cases: \gls{ULOHS} accident
			\end{itemize}
		\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Objectives}
		\textbf{Objectives}
		\begin{itemize}
			\item Verify the neutronics results in Moltres against Serpent
			\cite{leppanen_serpent_2015} with the \gls{MSFR} concept with six
			neutron energy groups
			\begin{itemize}
				\item Previous validation study has been performed with an
				MSRE-like model with two (fast/thermal) neutron energy groups
				\cite{lindsay_introduction_2018}
			\end{itemize}
			\item Demonstrate coupled neutronics/thermal-hydraulics simulations
			of the \gls{MSFR} concept using Moltres,
			\begin{itemize}
				\item with start-up, early-life, and equilibrium fuel
				compositions
				\item for steady state and transient cases: \gls{ULOHS} accident
			\end{itemize}
		\end{itemize}
\end{frame}
